Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2021-01-19 paper/main.tex
Added more coauthors and affiliations

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Hierarchically modelling dwarfs and subgiants]{
    Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology
    %TBC: Using machine learning of stellar models to constrain the Helium enrichment of low-mass \emph{Kepler} dwarfs in the solar neighbourhood
    }

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Oliver J. Hall,$^{4,1,2}$
\newauthor
Daniel Huber,
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
and To B. Confirmed
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
$^{4}$European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands\\
}

@@

% Abstract of the paper <= 250 words
\begin{abstract}
    With recent advances in modelling stars using high-precision asteroseismology, the systematic effects associated with our assumptions of stellar helium abundance ($Y$) and the mixing-length theory parameter ($\mlt$) are becoming more important. We apply a new method to improve the inference of stellar parameters for a sample of \emph{Kepler} dwarfs and subgiants across a narrow mass range ($0.8 < M < \SI{1.2}{\solarmass}$). In this method, we include a statistical treatment of $Y$ and the $\mlt$. We develop a hierarchical Bayesian model to encode information about the distribution of $Y$ and $\mlt$ in the population, fitting a linear helium enrichment law including an intrinsic spread around this relation and normal distribution in $\mlt$. We test various levels of pooling parameters, with and without solar data as a calibrator. When including the Sun as a star, we find the gradient for the enrichment law, $\Delta Y / \Delta Z = 1.05\substack{+0.28\\-0.25}$ and the mean $\mlt$ in the population, $\mu_\alpha = 1.90\substack{+0.10\\-0.09}$. While accounting for the uncertainty in $Y$ and $\mlt$, we are still able to report statistical uncertainties of 2.5 per cent in mass, 1.2 per cent in radius, and 12 per cent in age. Our method can also be applied to larger samples which will lead to improved constraints on both the population level inference and the star-by-star fundamental parameters. We show that more work is needed to study the validity of using the Sun as a calibrator for $Y$ and $\mlt$.
\end{abstract}

@@

\section{Introduction}
%%%%%%%%%%%%%%%%%%%%
%%% INTRODUCTION %%%
%%%%%%%%%%%%%%%%%%%%

@@

\section{Data}\label{sec:data}
%%%%%%%%%%%%
%%% DATA %%%
%%%%%%%%%%%%

@@

\section{Methods}\label{sec:meth}
%%%%%%%%%%%%%%%
%%% METHODS %%%
%%%%%%%%%%%%%%%

@@

\section{Results}\label{sec:res}
%%%%%%%%%%%%%%%
%%% RESULTS %%%
%%%%%%%%%%%%%%%

@@

\section{Discussion}\label{sec:dis}
%%%%%%%%%%%%%%%%%%
%%% DISCUSSION %%%
%%%%%%%%%%%%%%%%%%

@@

\section{Conclusion}
%%%%%%%%%%%%%%%%%%
%%% CONCLUSION %%%
%%%%%%%%%%%%%%%%%%

@@

\section*{Acknowledgements}

@@

% \section{Grid of stellar models}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{figures/context_grid.png}
%     \caption{The luminosity, $L$ against effeective temperature, $\teff$ of the sample of 81 \emph{Kepler} dwarfs and subgiants plot against a subset of the grid of stellar models computed in Section \ref{sec:grid}. The top plot is coloured by stellar surface metallicity and the bottom plot is coloured by stellar mass.}
%     \label{fig:data-grid}
% \end{figure}

\section{Training the ANN}\label{sec:apx-train}

@@

\section{The synthetic population}\label{sec:test-stars}

@@

\section{The Sun as a star}\label{sec:sun-res}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Hierarchically modelling dwarfs and subgiants]{%
    Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology
}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{%
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Oliver J. Hall,$^{4,1,2}$
\newauthor
Daniel Huber,$^{5}$
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
Sarbani Basu,$^{6}$
\newauthor
Will M. Farr,$^{7,8}$
Rafael A. Garc\'ia,$^{9}$
Ilya Mandel,$^{10}$
and Sean Matt$^{11}$
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
$^{4}$European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands\\
$^{5}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{6}$Department of Astronomy, Yale University, 52 Hillhouse Avenue, New Haven, CT 06511, USA\\
$^{7}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, New York 10010, USA\\
$^{8}$Department of Physics and Astronomy, Stony Brook University, Stony Brook, New York 11794, USA\\
$^{9}$AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, 91191, Gif-sur-Yvette, France\\
$^{10}$Monash Centre for Astrophysics, School of Physics and Astronomy, Monash University, Clayton, VIC 3800, Australia\\
$^{11}$Department of Physics and Astronomy, University of Exeter, Stocker Road, Exeter, EX4 4QL, UK
}

@@

% Abstract of the paper <= 250 words
\begin{abstract}
    With recent advances in modelling stars using high-precision asteroseismology, the systematic effects associated with our assumptions of stellar helium abundance ($Y$) and the mixing-length theory parameter ($\mlt$) are becoming more important. We apply a new method to improve the inference of stellar parameters for a sample of \emph{Kepler} dwarfs and subgiants across a narrow mass range ($0.8 < M < \SI{1.2}{\solarmass}$). In this method, we include a statistical treatment of $Y$ and the $\mlt$. We develop a hierarchical Bayesian model to encode information about the distribution of $Y$ and $\mlt$ in the population, fitting a linear helium enrichment law including an intrinsic spread around this relation and normal distribution in $\mlt$. We test various levels of pooling parameters, with and without solar data as a calibrator. When including the Sun as a star, we find the gradient for the enrichment law, $\Delta Y / \Delta Z = 1.05\substack{+0.28\\-0.25}$ and the mean $\mlt$ in the population, $\mu_\alpha = 1.90\substack{+0.10\\-0.09}$. While accounting for the uncertainty in $Y$ and $\mlt$, we are still able to report statistical uncertainties of 2.5 per cent in mass, 1.2 per cent in radius, and 12 per cent in age. Our method can also be applied to larger samples which will lead to improved constraints on both the population level inference and the star-by-star fundamental parameters.% We show that more work is needed to study the validity of using the Sun as a calibrator for $Y$ and $\mlt$.
\end{abstract}

@@

\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%

@@

\section{Data}\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% DATA %%%%%%%%%%%%%%%%%%

@@

\section{Methods}\label{sec:meth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%

@@

\section{Results}\label{sec:res}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%

@@

\section{Discussion}\label{sec:dis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%

@@

\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%

@@

\section*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGEMENTS %%%%%%%%%%%%%%%%%%

@@

\section{Training the ANN}\label{sec:apx-train}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% TRAINING THE ANN %%%%%%%%%%%%%%%%%%

@@

\section{The synthetic population}\label{sec:test-stars}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% THE SYNTHETIC POPULATION %%%%%%%%%%%%%%%%%%

@@

\section{The Sun as a star}\label{sec:sun-res}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% THE SUN AS A STAR %%%%%%%%%%%%%%%%%%
